%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\begin{document}%
\header{prakash}{venkat}%
       {web developer}%


% In the aside, each new line forces a line break
\begin{aside}
  \section{address}
    10567 National Blvd
    Los Angeles, CA 90034
    ~
    \href{mailto:prakash@asanet.com}{prakash@asanet.com}
    \href{http://prakashvenkat.com}{prakashvenkat.com}
  \section{languages}
    JavaScript
    Python
    Java
    LISP
    CSS3 \& HTML5
  \section{tools}
    Angular
    Postgres
    Docker
\end{aside}

\section{about}
Full-stack web developer. Programming junkie. Born and raised new jerseyian. World traveler. I've built web sites, interactive widgets,
RESTful APIs, chatrooms, data visualizations, anagram solvers, console applications,
HTML5 frameworks. If you're looking for something web-related, I'm your man.

\section{education}

\begin{entrylist}
  \entry
    {2006–2010}
    {GPA 3.8/4.0}
    {B.S. Economics with Honors}
    {University of Michigan}
\end{entrylist}

\section{experience}
\tabentry
  {11/2016 – Present}
  {Aspiration}
  {Sr. Full Stack}
  {Full stack developer at a Fintech company. Built cutting edge retail banking products that served customers needs while interfacing with obsolete ACH infrastructure. Automation, design, team management were my foci here. \\%
  \ind{1.5ex}{\textbf{Details:}}\\%
    \bulletlist
    {Designed and built a payment system for checks that
      \jdb{serviced an average of 200 customers a day. The system
      \jdb{was designed and built singlehandedly in 3 weeks}}}
    {Improved team productivity with a custom Slack bot.The bot
      \jdb{had the ability to automate deployments, post gifs,
      \jdb{and reply to chat messages chat messages with witty
      \jdb{banter.}}}}
    {Devoted significant time to creating a speedy and 
      \jdb{transparent build process. Wrote a number of
      \jdb{bash scripts to glue together several disparate projects.
      \jdb{On completion, a developer could build the entire api,
      \jdb{setup test databases, and run migrations with a single command.}}}}}
    {Migrated one of our frontend projects from Angular 1 
      \jdb{to Angular 2 (this was before Angular 4 was released).}}
    \hspace*{1.5ex}-\hspace{1ex}\emph{Organized various social events throughout the company 
      \jdb{to promote cross-team camraderie. Events consisted of 
      \jdb{a game night, movie night, yacht cruise through Marina 
      \jdb{Del Rey, and a White Elephant Gift Exchange.}}}}\\%
    \hspace*{1.5ex}-\hspace{1ex}\emph{Fostered cross-team projects to meet business goals. 
      \jdb{Worked with our Financial Operations team 
      \jdb{to reduce the amount of fraudulent transactions on our system.}}}
  }
\pagebreak
\tabentry
  {11/2015 – 9/2016}
  {Kargo Global}
  {Sr. Web Developer}
  {Lead Angular developer at a global adtech company. Developed tools that facilitate exchange between advertisers and publishers. Big on open source contributions. I build software that meets business needs.\\%
  \ind{1.5ex}{\textbf{Details:}}\\%
    \bulletlist
    {Modified core Angular modules to allow for inheritance\jdb{between controllers}}
    {Designed real-time visualizations of data that directly\jdb{improved the UX of an in-house WYSIWYG editor}}
    {Created a workflow tool that allowed members of the\jdb{development team to programmatically generate documentation}}
    {Built an interactive wizard that led clients \jdb{through the process of buying media}}
  }
\tabentry
  {11/2013 – 11/2015}
  {Adcade}
  {Sr. Web Developer}
  {Lead web developer at an advertising tech startup. Mastered fundamentals of web MVC/MVVM/MV* design. Delved into the guts of Angular-based web app development. Kept a library of reusable React components for a rainy day. Developed a set of HTML5 tools used to create rich, responsive interactive ads across all browsers and devices.\\%
  \ind{1.5ex}{\textbf{Details:}}\\%
    \bulletlist
    {Created a campaign management dashboard that \jdb{allowed users to monitor metrics and generate reports}}
    {Developed software for displaying HTML5 inside \jdb{mobile apps in accordance with the MRAID}\jdb{and VPAID specifications}}
    {Built canvas modules that played animations \jdb{and video with no lag on desktop or mobile devices}}
    {Led daily standups and managed sprints in order \jdb{to meet deadlines and deliver software on time}}
  }
\tabentry
  {01/2012 – 11/2013}
  {LearnBop Inc.}
  {Web Developer}
  {Lead front end developer at an education tech startup. I've developed everything from support chat to infographics to interactive UIs. My main project was the design and creation of an interactive lesson authoring tool that was used to generate 500+ lessons. It is still in use today.
  \ind{1.5ex}{\textbf{Details:}}\\%
    \bulletlist
    {Wrote libraries for rendering reactive UI elements \jdb{using a combination of Handlebars and Backbone}}
    {Developed a customer support chat application \jdb{utilizing websockets and longpolling}}
    {Wrote Simple Object Access Protocol web services \jdb{for fetching large XML responses}}
    {Gained familiarity with AWS tools like S3 Cloud Storage, \jdb{CloudFront, and ElasticBeanstalk}}
  }
\pagebreak
\tabentry
  {09/2011 – 12/2011}
  {Bloomberg}
  {Project Data Analyst}
  {Worked as an analyst on Bloomberg project Bgov. My job was to catalog local, state, and national politicians and draw relationships between their campaigns and their funding.\\%
  \ind{1.5ex}{\textbf{Details:}}\\%
    \bulletlist
    {Translated Excel spreadsheets into SQL tables}
    {Implemented text parsing algorithms using Regex}
    {Prototyped render engines for visualizing analyzed data}
    {Generated insights by defining relationships \jdb{between political platforms and donations}}
  }
\tabentry
  {09/2010 – 04/2011}
  {Hill \& Knowlton Global Public Relations}
  {Intern}
  {Intern for a digital public relations company. Among my many important duties were making copies and ordering lunch. Got a taste for various blogging engines, Drupal, Typepad, Blogger, the primary one being Wordpress.\\%
  \ind{1.5ex}{\textbf{Details:}}\\%
    \bulletlist
    {Designed and deployed Wordpress blogs}
    {Composed and edited copy for 100+ blog posts}
    {Created slide decks for use in client meetings}
    {Presented blog design to firm's technical \jdb{leadership weekly}}
  }

\section{public talks}

\begin{entrylist}
  \entry
    {June 2016}
    {JSLA: Constructing DSLs to Automate Automation}
    {\href{https://www.youtube.com/watch?v=qcF3omniwtY}{Link}}
    {Presented Vyuha, a DSL and toy compiler for describing deployment workflows.}
  \entry
    {July 2016}
    {PyGotham: Steganography using the Python Imaging Library (PIL)}
    {\href{https://goo.gl/wXvnT4/The_Colors_Duke_Steganography_using_the_Python_Imaging_Library_PIL.png}{Link}}
    {Showcased a pet project of mine, Pixcrypt, that concealed text inside images using steganography.}
  \entry
    {November 2016}
    {Codesmith: Shaking Dependency Graphs}
    {\href{}{Link}}
    {Walked the students at Codesmith through an algorithm for constructing and optimizing dependency graphs. The talk was inspired by my own desire to design a simple Javascript build system.}
  \entry
    {February 2017}
    {Codesmith: Exploring the Used Car Market Pt. 1}
    {\href{}{Link}}
    {Shed light on the dynamics of Los Angeles's used car market. Presented analysis of variations in price as a function of car type.}
  \entry
    {April 2017}
    {FullStack JS: Exploring the Used Car Market Pt. 2}
    {\href{https://www.meetup.com/SoCal-Full-Stack-JS/events/238047650/}{Link}}
    {Sequel to the first talk. Presented the eccentricities of the used car market as a function of car make.}
\end{entrylist}

\pagebreak

\section{side projects}

\begin{entrylist}

  \entry
    {Ongoing}
    {Car Research}
    {\href{}{Blog}}
    {Tracked the progression of used car price across various traits to get a feel for how the market works. Came up with a surprisingly accurate way to plot the depreciation of a car.}

\end{entrylist}

\section{awards}

\begin{entrylist}
  \entry
    {October 2014}
    {Finalist, Money 20/20 Hackathon}
    {\href{http://github.com/dopatraman/pixcrypt}{Pixcrypt}}
    {Concealed bitcoin wallet information inside pictures using steganography. Users could send sensitive bitcoin information to each other in the form of images, as opposed to verbose bitcoin addresses. Users could also embed bitcoin information in the world around them by taking photographs.}
  \entry
    {April 2013}
    {Finalist, Ghostery Hackathon}
    {\href{http://github.com/dopatraman/FalconExtension}{Falcon}}
    {Wrote a browser extension that throttled the number of extraneous requests made before rendering a website. Was able to demonstrably cut load times for sites by up to 10\%.}
\end{entrylist}

\section{hobbies}

  - Surfing\\%
  - Snowboarding\\%
  - Photography\\%
  - Traveling\\%
  - Brewing Beer\\%

\end{document}
